---
title: "Potencial Cariogênico"
subtitle: "Análise de Dados Longitudinais"
author: "Daniel de Amaral"
date: "`r str_to_title(format(Sys.time(), '%b, %Y'))`"
bibliography: ./assets/references/references.bib
output: 
  ioslides_presentation:
    logo: ./assets/figures/logo.png
    css: ./assets/css/styles.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r load.data}
potencialc <- tibble(voluntario = rep(1:21, 2),
                     potencial = c(6, 0, 0, 3.37, 0, 14.25, 0, 0, 0, 0,
                                   0.37, 14.25, 0, 14.44, 0, 0, 0, 0, 0,
                                   12.37, 0, 3.37, 1.5, 10.69, 8.44, 2.5,
                                   5.25, 5.5, 0.37, 1.5, 16.5, 0, 15.94,
                                   5.25, 0, 12.25, 9.25, 9, 8.5, 9, 22.5, 0.75),
                     momento = c(rep('Antes', 21), rep('Depois', 21)))
```

## R Markdown

This is an R Markdown presentation [@RCoreTeam]. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

## References {.allowframebreaks}